Identifying regime transitions for water governance: Take the Yellow River Basin in China as case

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
docs(paper): :memo: 回答审稿人引言增加指标叙述

>>>>

\AR{} Thanks for valuable suggestion. We now added a whole paragraph to the introduction:  % TODO 检查引用

\begin{quote}
    Responding the questions for better water governance practices, previous studies can divide into two categories of comprehensive indicators by focusing on water systems or governance systems.
    From the governance side, an integrated index can explicitly denote what practices are effecting water governance.
    However, a comprehensive and detailed list of the key components for assessment of water governance is rare, hence quantitative studies usually propose indexes by using proxy dataset of human activities as a simpler way~\cite{varis2019}.
    A qualitative approach to the assessment of water governance can list more elements regarding to water governance, where OECD's index and assessment dataset are the most widely used. % todo cite OECD
    From the water side, intuitive indexes can provide an embodiment of governance outcomes.
    Water stress is the most widely concerned aspect, which has been far developed in comprehensive index when incorporating human's regulation step by step.
    As instances, traditional water stress index only demands and supply, water scarcity index by involving accessibility, and SFV-index further integrated flexibility.
    These easy-to-use indexes of water stress, however, seem to have difficulty in providing a comprehensive characterization of the above water governance aspects without concerning its social usage (i.e., water use purpose and water allocation).
    Standing from water side for comprehensively quantify governance outcomes, here we aim to develop an integrated water governance index to identify its changes by involving apportions of water uses between regions and sectors.
\end{quote}
